Social Conditions of Fear

### 2023-11-22 scripts/manuscript.qmd
mice imputation

```{r}
#| label: coding all missing data as NA 
# NOT WORKING - Need to troubleshoot
missing_vec <- c(".i:  Inapplicable", ".n:  No answer", ".d:  Do not Know/Cannot Choose", ".s:  Skipped on Web")

@@

#data_complete <- mice(data, m=5)

#summary(complete(data,1))

@@

```{r}
#| label: mice imputations to deal with missing data

#data_complete <- mice(no_na_data, m=5)

#summary(complete(data_complete,1))
```

```{r}
#| label: recode-variables
tidydata <- data %>% 
  mutate(fear = 
           case_when( fear == ".i:  Inapplicable" | fear == ".n: No answer" | 
                        fear == ".d: Do not Know/Cannot Choose" |fear == ".s: Skipped on Web" ~ NA_character_, 
                      fear == "YES" ~ "yes", 
                      fear == "NO" ~ "no")) %>% 
  filter(fear == "yes" | fear == "no") %>% 
  mutate(racecombo = 
           case_when(racerank1 == "White" ~ "White",
                     racerank1 == "Black or African American" ~ "Black",
                     racerank1 == "Hispanic" ~ "Hispanic",
                     racerank1 == "Asian Indian" | racerank1 ==  "Chinese" |
                       racerank1 ==  "Filipino" | racerank1 ==  "Japanese" | 
                       racerank1 ==  "Korean" |  racerank1 ==  "Vietnamese" |
                       racerank1 ==  "Other Asian" ~ "Asian",
                     racerank1 == "American Indian or Alaska Native" ~ "AIAN",
                     racerank1 == "Guamanian or Chamorro" | racerank1 == "Samoan" |
                       racerank1 == "Other Pacific Islander" ~ "NHPI",
                      racerank1 == "Some other race" ~ "Other",
                     .default = NA_character_)) %>% 
  filter(!is.na(racecombo)) %>% 
  select("id", "age", "sex", "sexnow1", "sexornt", "degree", "attend", "raclive", "happy", "health", "helpful", "fair", "trust", "fear",  "partnrs5", "racecombo", "uscitzn", "dwelown")

@@

>>>>

```{r}
#| label: coding all missing data as NA

missing_vec <- c(".i:  Inapplicable", ".n:  No answer", ".d:  Do not Know/Cannot Choose", ".s:  Skipped on Web")

@@

@@

```{r}
#| label: mice imputation

complete5 <- mice(na_data, 
                 m=5, 
                 seed = 25)

complete <- complete(complete5,1)

@@

```{r}
#| label: recode-variables
tidydata <- na_data %>% 
  filter(!is.na(fear)) %>% 
  mutate(racecombo = 
           case_when(racerank1 == "White" ~ "White",
                     racerank1 == "Black or African American" ~ "Black",
                     racerank1 == "Hispanic" ~ "Hispanic",
                     racerank1 == "Asian Indian" | racerank1 ==  "Chinese" |
                       racerank1 ==  "Filipino" | racerank1 ==  "Japanese" | 
                       racerank1 ==  "Korean" |  racerank1 ==  "Vietnamese" |
                       racerank1 ==  "Other Asian" ~ "Asian",
                     racerank1 == "American Indian or Alaska Native" ~ "AIAN",
                     racerank1 == "Guamanian or Chamorro" | racerank1 == "Samoan" |
                       racerank1 == "Other Pacific Islander" ~ "NHPI",
                      racerank1 == "Some other race" ~ "Other")) %>% 
  select("id", "age", "sex", "sexnow1", "sexornt", "degree", "attend", "raclive", "happy", "health", "helpful", "fair", "trust", "fear",  "partnrs5", "racecombo", "uscitzn", "dwelown")
